Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-02-04 paper/paper.tex
some music net description

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model, \citep{citation_needed}, and its $\cplx$-counterpart, fit
on the full training split of $60k$ colour $32\times32$ images, and use only raw image
input features (\texttt{raw}).

@@

\citet{trabelsi_deep_2017} designed a complex-valued network that achieved SOTA results
on the music-transcription task on MusicNet, \citep{thickstun_learning_2017}.

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017

% mention 44khz to 11khz downsampling and the extraction of the originally recommended test set
% and the validation set chosen by Trabelsi et al.

@@

The set up of the experiment is thus:
Each full three-stage run is replicated five times take random effects into account, e.g.
random network initialization prior to ``dense'' stage, randomly picked $1000$ batches from
the sample during SGD.

>>>>

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model, \citep{simonyan_very_2015}, and its $\cplx$-counterpart, fit
on the full training split of $60k$ colour $32\times32$ images, and use only raw image
input features (\texttt{raw}).

@@

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
MusicNet, \citep{thickstun_learning_2017}, is an annotated audio dataset, consisting of $330$
compositions from the public domain. Similarly to \citep{trabelsi_deep_2017}, we use this
dataset for automatic music transcription task and study the $1d$ VGG-like $\cplx$-convent
proposed therein. Similarly to this study, we downsample the sound from 44.1kHz to 11kHz,
retaining only $84$ out of $128$ labels, and hold-out the same validation and test splits.
During each training epoch we sample $1000$ mini-batches of the remaining $321$ compositions
thus: a random full window of $4096$ samples is picked within each waveform and transformed
from $\real$ to $\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the
window.

We use training from sec.~\ref{sub:fitting_and_compression} with epochs lasting for $12$,
$32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
stage. Preliminary experiments with the model without sparsification have shown that early
stopping almost always terminated the training process within the first $10-20$ epochs,
and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
in \citep{trabelsi_deep_2017}. Besides staged training and shorter ``dense'' stage, other
important deviations from their setup include:
\begin{itemize}
  \item shifting lower frequencies to the centre of the window to maintain locality after
  applying FFT (much like in sec.~\ref{sub:mnist_like_datasets})
  \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_compression})
\end{itemize}
Each full three-stage experiment is replicated five times to take random effects into account,
e.g. random network initialization prior to ``dense'' stage, randomization of batches within
each epoch during SGD, and stochasticity of Bayesian forward pass at ``sparsify'' stage.

@@
